Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

dfs <- df %>% group_by(publication_year) %>%
              summarise(mean_title_length = mean(title_length, na.rm = TRUE))

p <- ggplot(dfs, aes(x = publication_year, y = mean_title_length)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place), size = 2) +
       xlab("Publication year") +
       ylab("Title length (characters)") +
       ggtitle("Mean title length in selected cities") +
       guides(color = guide_legend(title = "Place", reverse = TRUE))
print(p)
```

>>>>

p <- ggplot(df, aes(x = publication_year, y = mean_title_length)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place), size = 2) +
       xlab("Publication year") +
       ylab("Title length (characters)") +
       ggtitle("Mean title length in selected cities") +
       guides(color = guide_legend(title = "Place", reverse = TRUE))
print(p)
```
